Liveness-Based Garbage Collection for Lazy Languages

### 2016-04-16 paper/cfg-to-nfa.tex
fixed fig 7&8

\input{main-pgm1}
For the main  program in Figure~\ref{fig:main-pgm1}, the liveness corresponding
to  the  variable   \var{\Lanv{\pa}{}} at $\pi_{10}$ is given by 
$\var{\Lanv{\pa}{}} \rightarrow \clazy \bcar \var{\Df{\length}{1}}$.
The  DFA   corresponding to this grammar is 
\dfaE. 
As there is no $\acar$ symbol to cancel the $\bcar$ symbol in the automaton, no 
$\epsilon$ edges are added and the $\bcar$ edge is deleted to get 
\dfaF.
We finally do the $\clazy$ simplification and notice that there is no path to a final state. 
Thus, we delete the $\clazy$ edge without marking any state as final giving the final automata for 
$\var{\Lanv{\pa}{}}$ as 
\dfaG.
The final automaton does not
accept any forward paths, reflecting  the lazy nature of our language.
Since
\length\ does not  evaluate the elements of  the argument list,
the  closure for  \pa\ is  never evaluated  and is  reclaimed whenever
liveness-based GC triggers beyond $\pi_9$.

>>>>

%\input{main-pgm1}
For the main  program in Figure~\ref{fig:mot-example2-a}, the liveness corresponding
to  the  variable   \var{\Lanv{\pa}{}} at $\pi_{10}$ is given by 
$\var{\Lanv{\pa}{}} \rightarrow \clazy \bcar \var{\Df{\length}{1}}$.
The  DFA   corresponding to this grammar is 
\dfaE. 
As there is no $\acar$ symbol to cancel the $\bcar$ symbol in the automaton, no 
$\epsilon$ edges are added and the $\bcar$ edge is deleted to get 
\dfaF.
We finally do the $\clazy$ simplification and notice that there is no path to a final state. 
Thus, we delete the $\clazy$ edge without marking any state as final giving the final automata for 
$\var{\Lanv{\pa}{}}$ as 
\dfaG.
The final automaton does not
accept any forward paths, reflecting  the lazy nature of our language.
Since
\length\ does not  evaluate the elements of  the argument list,
the  closure for  \pa\ is  never evaluated  and is  reclaimed whenever
liveness-based GC triggers beyond $\pi_9$.
